Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
RQ1 results intro

%% Check what willy wrote.
%%Explain structure of this section around the RQ and a summary of it. Table with the percentages from both us and her.

Specifically we found that 53.8\% of the changes were enhancive changes, 7.7\% were adaptive and the remaining 38.5\% were changes specifically aimed at improving the maintainability of the API.

>>>>

%% Check what willy wrote.
%%Explain structure of this section around the RQ and a summary of it. Table with the percentages from both us and her.
In order to answer \textbf{RQ1}, we categorised the changes based on the 12 maintenance categories \cite{chapin2001types}. Initially, we created predictions of the changes from inspecting the source code and accompanying documentation. Following the interview, we compared our predictions with the actual motive which was deduced from the interviewee's reasoning. Table \ref{table:Categories} shows the predicted and actual maintenance categories.

The changes have been divided up into four specific categories, namely: new, modified, removed and general trends. New and modified changes concern additions of or modifications to modules and removed changes is functionality which have been removed entirely without being deprecating or replaced by new implementations. General trends are broad changes which do not directly affect functionality.
